% !TEX root = paper.tex
% !TEX encoding = UTF-8 Unicode

\subsection{English to German}

With the goal of restructuring English source sentences to have more German-like structure, we define the following transformation rules:

\begin{enumerate}
%
\item Detect all clauses in a sentence which might require transformation.
      We selected spans of text, which were labeled as S or SBAR by the parser.
      We do not include clauses which begin with ``to''.
%      
\item For each clause, we apply the following rules in order :
%
\begin{enumerate}
%
	\item If there exists a verb phrase (detected by a shallow parser) with ``to'', we move the remaining portion of the verb phrase (starting with token ``to'') to the end of the clause.
%
	\item If there exists a verb phrase (detected by a shallow parser) with a token with VBN part of speech tag, we move the remaining portion of the verb phrase (starting with VBN token) to the end of the clause.
%
	\item If there exists a verb phrase (detected by a shallow parser) starting with a modal verb, we leave the modal verb but move the rest of the verb phrase to the end of the clause.
%
\end{enumerate} 
%
\end{enumerate}
%
We used a state-of-the-art shallow parser \cite{PunyakanokRo01} in conjunction with a constituent parser \cite{socher-EtAl:2013:ACL2013} to implement the above transformation rules.
%
For the purposes of the English-German language pair, we pre-process all English data into equivalent English$^\prime$ data using the above transformation rules.

We train a German language model on the German side of the Europarl, Common Crawl, and News Commentary corpora, and a translation model on the English$^\prime$-German Europarl corpus.
%
Our development set for tuning was the WMT newstest data from 2008--2014.
%
Results for the WMT newtest-2015 data set under the baseline (en-de) and restructured (en$^\prime$-de) conditions are shown in Table~\ref{tab:ende}.

\begin{table}[!h]
\center 
{
	\begin{tabular}{|l|l|l|l|}
	\hline
	System        & BLEU  & BLEU-cased & TER   \\ \hline
%	en-de (dev)  & 15.1  & 14.6      & 0.889 \\ \hline
%	en$^\prime$-de (dev)       & 18.9  & 19.2      & 0.686 \\ \hline \hline
	en-de & 16.6  & 16.3      & 0.933 \\ \hline
	en$^\prime$-de      & 17.9  & 17.2       & 0.731 \\ \hline
%	Best-Test     & 25.2  & 24.9       & 0.665 \\ \hline
	\end{tabular}
}
\caption{Results for English and English$^\prime$ translated into German.}
\label{tab:ende}
\end{table}
