\documentclass[11pt]{article}
\usepackage{graphicx,fancyhdr,verbatim}
\usepackage[margin=1.0in]{geometry}

\begin{document}

\textbf{Nationality Detection I}

~\\
I disagree with this statement for several reasons.  While it can be argued that
having a part-time job is valuable preparation for a full-time job that the
student will acquire upon graduation, this is often not the case. In many cases,
any part-time employment obtained by a student will be in a field, and of a
nature that is completely unrelated to that of their chosen course of study. For
example, a student studying engineering has very little valuable experience to
gain from working as a waiter in a restaurant.  Moreover, there is ample reason
for students to not engage in part-time employment. Such a job can often mean a
considerable amount of additional stress on top of that created by their
studies. The stress of studying can also be increased, as there is less time
available to accomplish it. Additionally, many part-time jobs can leave one
tired, and thus unable to focus effectively on their studies, resulting in a
lower quality of school work being produced.  Therefore, if a part-time job
related to the student's field of study can be found (such as an internship),
then it may be worth pursuing, but otherwise part-time employment should only be
sought if it is necessary for financial reasons (i.e., to pay tuition fees).

\begin{verbatim}
<s> PRP VBP IN DT NN IN JJ NNS . </s>

<s> IN PRP MD VB VBN IN VBG DT JJ NN VBZ JJ NN IN DT JJ NN IN DT NN MD VB IN NN
, DT VBZ RB RB DT NN . </s> <s> IN JJ NNS , DT JJ NN VBN IN DT NN MD VB IN DT NN
, CC IN DT NN WDT VBZ RB JJ TO DT IN PRP$ VBN NN IN NN . </s>

<s> IN NN , DT NN VBG NN VBZ RB JJ JJ NN TO VB IN VBG IN DT NN IN DT NN . </s> 

...
\end{verbatim}

\begin{verbatim}

(S(NP(PRP))(VP(VBP)(PP(IN)(NP(NP(DT)(NN))(PP(IN)(NP(JJ)(NNS))))))(.))

(S(SBAR(IN)(S(NP(PRP))(VP(MD)(VP(VB)(VP(VBN)(SBAR(IN)(S(S(VP(VBG)(NP(DT)(JJ)(NN))))
(VP(VBZ)(NP(NP(JJ)(NN))(PP(IN)(NP(DT)(JJ)(NN))))(SBAR(IN)(S(NP(DT)(NN))(VP(MD)(VP(VB)
(PP(IN)(NP(NN)))))))))))))))(,)(NP(DT))(VP(VBZ)(ADVP(RB)(RB))(NP(DT)(NN)))(.))

(S(PP(IN)(NP(JJ)(NNS)))(,)(NP(NP(DT)(JJ)(NN))(VP(VBN)(PP(IN)(NP(DT)(NN)))))(VP(MD)
(VP(VB)(PP(PP(IN)(NP(DT)(NN)))(,)(CC)(PP(IN)(NP(NP(DT)(NN))(SBAR(WHNP(WDT))(S(VP(VBZ)
(ADJP(RB)(JJ)(PP(TO)(NP(NP(DT))(PP(IN)(NP(NP(PRP$)(JJ)(NN))(PP(IN)
(NP(NN))))))))))))))))(.))

...
\end{verbatim}

\newpage

\textbf{Nationality Detection II}

~\\
In my opinion, it's important for students to have a part-time job. But I
argue that the job must be a proper part-time job. There are many advantages
for a student to have a proper part-time job. For instance, a proper part-time
job can help students to realize that no success comes from noting. It also
enables students to be independent and build up their self-confidence. In
addition, a proper part-time can make the students out of the ivory tower and
give them lots of opportunities to know more of themselves and the society. In
the same time, students can realize their personal value in society by having
a proper part-time job.  Of course, as we all known, everything has two sides.
If we do not know the balance between part-time and learning, something bad
will occur to us. In other words, an improper part-time job will bring many
disadvantages to us. For example, an improper part-time job must occupy
student's time and make them just pay their attention on money but not
what they should to learn.  In a word, a part-time job is important for the
students, but the students must keep a good balance between part-time and
their learning.  

\begin{verbatim}
<s> IN PRP$ NN , PRP VBZ JJ IN NNS TO VB DT JJ NN . </s>

<s> CC PRP VBP IN DT NN MD VB DT JJ JJ NN . </s>

<s> EX VBP JJ NNS IN DT NN TO VB DT JJ JJ NN . </s>

...
\end{verbatim}

\begin{verbatim}

(S(PP(IN)(NP(PRP$)(NN)))(,)(NP(PRP))(VP(VBP)(ADJP(JJ)(PP(IN)(NP(NNS)(S(VP(TO)
(VP(VB)(NP(DT)(JJ)(NN)))))))))(.))

(S(CC)(NP(PRP))(VP(VBP)(SBAR(IN)(S(NP(DT)(NN))(VP(MD)(VP(VB)(NP(DT)(JJ)(JJ)
(NN)))))))(.))

(S(NP(EX))(VP(VBP)(NP(NP(JJ)(NNS))(PP(IN)(NP(DT)(NN)(S(VP(TO)(VP(VB)(NP(DT)
(JJ)(JJ)(NN)))))))))(.))

...
\end{verbatim}

\newpage

\textbf{Nationality Detection III}

~\\
I agree this opinion that part-time job is important for college school
students, because I studied a lot of thing with my part-time job.   At first,
the communication skill is necessary to work. We must talk to owner and
companion, although it is not so necessary to talk to others at college
school. We must talk to our guests too. We can get good communication skill
with working. we can many variety friends too. At working place, there are
many peoples. Their age or environment who grow up is different from
yourselves. When you get along with them, you know new inspiration and it will
be useful thing.  Second, the experience get money from working is important
for our life of college school student. We will have to make a effort to get a
good job. For these difficult activities, part-time jobs are practice. We must
appeal ourselves to owners both of them to get work. If we get part-time job,
this success is turned into our confidence.  Third, many University student
want more money. Someone need money because play with their friends. Someone
need for traveling. Someone need for hobbies. Someone need for eating enough.
Part-time job is best for us to make money.

\begin{verbatim}
<s> PRP VBP DT NN WDT JJ NN VBZ JJ IN NN NN NNS , IN PRP VBD DT NN IN NN IN
PRP$ JJ NN . </s>

<s> IN RB , DT NN NN VBZ JJ TO VB . </s>

<s> PRP MD VB TO NN CC NN , IN PRP VBZ RB RB JJ TO VB TO NNS IN NN NN . </s>

...
\end{verbatim}

\begin{verbatim}
(S(NP(PRP))(VP(VBP)(NP(DT)(NN))(SBAR(IN)(S(NP(JJ)(NN))(VP(VBZ)(ADJP(JJ)(PP(IN)
(NP(NN)(NN)(NNS)))))))(,)(SBAR(IN)(S(NP(PRP))(VP(VBD)(NP(NP(DT)(NN))(PP(IN)(NP(NN))))
(PP(IN)(NP(PRP$)(JJ)(NN)))))))(.))

(S(PP(IN)(NP(JJ)))(,)(NP(DT)(NN)(NN))(VP(VBZ)(ADJP(JJ)(S(VP(TO)(VP(VB))))))(.))

(S(NP(PRP))(VP(MD)(VP(VB)(PP(TO)(NP(NN)(CC)(NN)))(,)(SBAR(IN)(S(NP(PRP))(VP(VBZ)
(RB)(ADJP(RB)(JJ)(S(VP(TO)(VP(VB)(PP(TO)(NP(NP(NNS))(PP(IN)(NP(NN)(NN))))))))))))))(.))

...
\end{verbatim}

\newpage

\textbf{Sentiment Analysis I}

~\\

I went and saw this movie last night after being coaxed to by a few friends of
mine. I 'll admit that I was reluctant to see it because from what I knew
of Ashton Kutcher he was only able to do comedy.  I was wrong. Kutcher played
the character of Jake Fischer very well, and Kevin Costner played Ben Randall
with such professionalism. The sign of a good movie is that it can toy with our
emotions.  This one did exactly that. The entire theater (which was sold out)
was overcome by laughter during the first half of the movie, and were moved to
tears during the second half. While exiting the theater I not only saw many
women in tears, but many full grown men as well, trying desperately not to let
anyone see them crying. This movie was great, and I suggest that you go see it
before you judge.

\begin{verbatim}

<s> PRP VBD CC VBD DT NN JJ NN IN VBG VBN TO IN DT JJ NNS IN NN . </s>

<s> PRP MD VB IN PRP VBD JJ TO VB PRP IN IN WP PRP VBD IN NNP NNP PRP VBD RB JJ
TO VB NN . </s>

<s> PRP VBD JJ . </s>

...
\end{verbatim}

\begin{verbatim}
(S(NP(PRP))(VP(VBD)(CC)(VBD)(NP(DT)(NN))(NP-TMP(JJ)(NN))(PP(IN)(S(VP(VBG)
(VP(VBN)(S(VP(TO)))(PP(IN)(NP(NP(DT)(JJ)(NNS))(PP(IN)(NP(NN))))))))))(.))

(S(NP(PRP))(VP(MD)(VP(VB)(SBAR(IN)(S(NP(PRP))(VP(VBD)(ADJP(JJ)(S(VP(TO)
(VP(VB)(NP(PRP))(PP(RB)(IN)(SBAR(WHNP(WP))(S(NP(PRP))(VP(VBD)(SBAR(S(PP
(IN)(NP(NNP)(NNP)))(NP(PRP))(VP(VBD)(ADVP(RB))(ADJP(JJ)(S(VP(TO)(VP(VB)
(NP(NN))))))))))))))))))))))(.))

(S(NP(PRP))(VP(VBD)(ADJP(JJ)))(.))

...
\end{verbatim}

\newpage

\textbf{Sentiment Analysis II}

~\\

Story of a man who has unnatural feelings for a pig.  Starts out with a opening
scene that is a terrific example of absurd comedy.  A formal orchestra audience
is turned into an insane , violent mob by the crazy chantings of it's singers.
Unfortunately it stays absurd the WHOLE time with no general narrative
eventually making it just too off putting.  Even those from the era should be
turned off.  The cryptic dialogue would make Shakespeare seem easy to a third
grader.  On a technical level it 's better than you might think with some good
cinematography by future great Vilmos Zsigmond.  Future stars Sally Kirkland and
Frederic Forrest can be seen briefly.

\begin{verbatim}
<s> NNP IN DT NN WP VBZ JJ NNS IN DT NN . </s>

<s> VBZ RP IN DT NN NN WDT VBZ DT JJ NN IN JJ NN . </s>

<s> DT JJ NN NN VBZ VBN IN DT JJ , JJ NN IN DT JJ NNS IN PRP VBZ NNS . </s>

...
\end{verbatim}

\begin{verbatim}
(NP(NP(NNP))(PP(IN)(NP(NP(DT)(NN))(SBAR(WHNP(WP))(S(VP(VBZ)(NP(NP(JJ)(NNS))
(PP(IN)(NP(DT)(NN)))))))))(.))

(S(VP(VBZ)(PRT(RP))(PP(IN)(NP(NP(DT)(NN)(NN))(SBAR(WHNP(WDT))(S(VP(VBZ)
(NP(NP(DT)(JJ)(NN))(PP(IN)(NP(JJ)(NN))))))))))(.))

(S(NP(DT)(JJ)(NN)(NN))(VP(VBZ)(VP(VBN)(PP(IN)(NP(DT)(ADJP(JJ)(,)(JJ))(NN)))
(PP(IN)(NP(NP(DT)(JJ)(NNS))(PP(IN)(NP(NP(PRP)(POS))(NNS)))))))(.))

...
\end{verbatim}

\newpage

\textbf{Essay Scoring I}

~\\

I think that we should have computers.  Because it help us find pleopl and it
help us talk to peopl and it help you srech thing too I can have a brother that
I never knew before then you can find that brother.  Then I can talk to my
firend online if I go to myspace or @CAPS1 because you can in @MONTH1 be have
firend on myspace , and by srech this you can find new thins and you can look up
this like weather in a different country or state I can find out how cold it is
in taxes and you can srech an up to see how old it can be.  Or how old it can
get.

\begin{verbatim}

<s> PRP VBP IN PRP MD VB NNS . </s>

<s> IN PRP VB PRP VB NN CC PRP VB PRP VB TO NN CC PRP VB PRP VBP NN RB PRP MD VB DT NN
IN PRP RB VBD IN RB PRP MD VB IN NN . </s>

<s> RB PRP MD VB TO PRP$ JJ NN IN PRP VBP TO VB CC NN IN PRP MD IN NN VB VBP VBN
IN NN , CC IN NN DT PRP MD VB JJ NNS CC PRP MD VB RP DT IN NN IN DT JJ NN CC NN
PRP MD VB RP WRB JJ PRP VBZ IN NNS CC PRP MD VB DT RB TO VB WRB JJ PRP MD VB . </s>

...
\end{verbatim}

\begin{verbatim}

(S(NP(PRP))(VP(VBP)(SBAR(IN)(S(NP(PRP))(VP(MD)(VP(VB)(NP(NNS)))))))(.))

(S(SBAR(IN)(S(S(NP(PRP))(VP(VBP)(S(NP(PRP))(VP(VB)(ADJP(JJ))))))(CC)(S(NP(PRP))(VP(VBP)
(SBAR(S(S(NP(PRP))(VP(VBP)(S(VP(TO)(VP(VB))))))(CC)(S(NP(PRP))(VP(VBP)(SBAR(S(NP(PRP))
(VP(VBP)(NP(NN))(ADVP(RB)))))))))))))(NP(PRP))(VP(MD)(VP(VB)(NP(DT)(NN))(SBAR(IN)
(S(NP(PRP))(ADVP(RB))(VP(VBD)(SBAR(IN)(S(ADVP(RB))(NP(PRP))(VP(MD)(VP(VB)(NP(DT)
(NN)))))))))))(.))

(S(RB)(NP(PRP))(VP(MD)(VP(VB)(PP(TO)(NP(PRP$)(JJ)(JJ)))(SBAR(SBAR(IN)(S(NP(PRP))(VP(VBP)
(S(VP(TO)(VP(VB)))))))(CC)(SBAR(X(SYM))(S(S(S(NP(NP(NNP))(SBAR(IN)(S(NP(PRP))(VP(MD)
(PP(IN)(NP(NNP)(NNP)))(VP(VB))))))(VP(VBP)(VP(VBN)(PP(IN)(NP(NN))))))(,)(CC)(S(PP(IN)
(NP(NN)))(S(NP(DT)(PRP))(VP(MD)(VP(VB)(NP(JJ)(NNS)))))(CC)(S(NP(PRP))(VP(MD)(VP(VB)
(PRT(RP))(NP(NP(DT)(JJ)(NN))(PP(IN)(NP(NP(DT)(JJ)(NN)(CC)(NN))(SBAR(S(NP(PRP))(VP(MD)
(VP(VB)(PRT(RP))(SBAR(WHADJP(WRB)(JJ))(S(NP(PRP))(VP(VBZ)(PP(IN)(NP(NNS))))))))))
))))))))(CC)(S(NP(PRP))(VP(MD)(VP(VB)(NP(DT)(RB))(S(VP(TO)(VP(VB)(SBAR(WHADJP(WRB)
(JJ))(S(NP(PRP))(VP(MD)(VP(VB))))))))))))))))(.))

...
\end{verbatim}

\newpage

\textbf{Essay Scoring II}

~\\

Dear @ORGANIZATION1, Computers these days have made positive changes to all of
our every day lives.  People have made beter connections with family and
friends, and even have the ability to make new ones.  While social networks are
great and all, computers can also make work extremely easy and
proffesional-looking. They can also perfect the skill of hand-eye coordination.
But with that in mind, is the computer truly a harmful or helpful device?
Sometimes we wonder where our long lost friends and relatives have gone and how
they are.  Well, with the computer and internet access, you can easily contact
them through great social networks such as @CAPS1. I hear it all the time from
everyone that reunions have been made, and friends have been reunited.  And
reuniting friends, you can also make new ones with a simple click of a button.
Isn't making more friends and reconnecting so easy now?

Computers nowadays offer wonderful software from @ORGANIZATION2 that can make
making slideshows, projects, and reports far easier. I remember making a
@CAPS2 with my best friend back when we were in @NUM1 grade. All we did was
take the pictures, upload them to his laptop, and then we added captions to
all of the pictures.  We did an amazing, professional job on the project and
received an A-.  Though I understand that in the process of computer-usage,
people hardly find time outdoors, the technological advance will enhance
hand-eye coordination.  Imagine this: You're up at bat in a baseball game.
@NUM2 strikes and @NUM3 balls is your count.  Everyone is cheering you on. The
pitcher pitches the ball and wham!  You swing that bat and hit yourself a
homerun!  Do you know what skill was used to hit that ball?  That's right ---
hand-eye coordination.  So now while everyone is wondering what sort of effect
the computer has, remember how easy that work was for me.

Also think back to that baseball player.  You know , the one that hit the
homerun using hand-eye coordination.  But most importantly remember how easy it
would be to contact the ones you love most and keep closest to you.  The
computer is a positive advance in society , and everyone should be assured so!

\begin{verbatim}
<s> NNP NNP , NNP DT NNS VBP VBN JJ NNS TO DT IN PRP$ DT NN VBZ . </s>

<s> NNS VBP VBN JJR NNS IN NN CC NNS , CC RB VBP DT NN TO VB JJ NNS . </s>

<s> IN JJ NNS VBP JJ CC DT , NNS MD RB VB NN RB JJ CC JJ . </s>

...
\end{verbatim}

\begin{verbatim}
(S(NP(NP(NNP)(NNP)(NNP))(,)(NP(NNS)))(NP-TMP(DT)(NNS))(VP(VBP)(VP(VBN)
(NP(JJ)(NNS))(PP(TO)(NP(NP(DT))(PP(IN)(NP(PRP$)(NP(NP(DT)(NN))(NP(NNS)))))))))(.))

(S(NP(NNS))(VP(VBP)(VP(VP(VBN)(NP(NN)(NNS))(PP(IN)(NP(NN)(CC)(NNS))))(,)(CC)
(ADVP(RB))(VP(VB)(NP(DT)(NN)(S(VP(TO)(VP(VB)(NP(JJ)(NNS)))))))))(.))

(S(SBAR(IN)(S(NP(JJ)(NNS))(VP(VBP)(ADJP(JJ)(CC)(RB)))))(,)(NP(NNS))(VP(MD)(ADVP(RB))
(VP(VB)(S(NP(NN))(ADJP(RB)(JJ)(CC)(JJ)))))(.))

...
\end{verbatim}

\end{document}
