\makecite{Ando and Zhang}{2005}{aso}{Ando, R. and Zhang, T. 2005. A Framework for Learning Predictive Structures from Multiple Tasks and Unlabeled Data. \emph{In the Journal of Machine Learning Research}, 1817-53}
\makecite{Blanchard, Tetreault, Higgins, Cahill, and Chodorow}{2013}{toef11}{Blanchard, D. and Tetreault, J. and Higgins, D. and Cahill, A and Chodorow, M. 2013. TOEF11: A Corpus of Non-Native English. \emph{Technical Report, Educational Testing Service}}
\makecite{Blei, Ng, and Jordan}{2003}{lda}{Blei, D. and Ng, A. and Jordan, M. 2003. Latent Dirichlet Allocation. \emph{In the Journal of Machine Learning Research}, 993-1022}
\makecite{Blunsom and Cohn}{2010}{tsgs}{Blunsom, P. and Cohn, T. 2010. Unsupervised Induction of Tree Substitution Grammars for Dependency Parsing. \emph{In Proceedings of the 2010 Conference on Empirical Methods in Natural Language Processing}, 1204-13}
\makecite{Bobicev}{2013}{ppm-bobicev}{Bobicev, V. 2013. Native Language Identification with PPM. \emph{In Proceedings of the Eighth Workshop on Innovative Use of NLP for Building Educational Applications}, 180-87}
\makecite{Boisson, Kao, Wu, Yen, and Chang}{2013}{linggle}{Boisson, J. and Kao, T. and Wu, J. and Yen, T. and Chang, J. 2013. Linggle: a Web-scale Linguistic Search Engine for Words in Context. \emph{In Proceedings of Association for Computational Linguistics (Conference System Demonstrations)}, 139-44}
\makecite{British Council}{2014}{british-council}{British Council 2014. How Many People Speak English? From {\url{http://www.britishcouncil.org/learning-faq-the-english-language.htm}}}
\makecite{Brockett, Dolan, and Gamon}{2006}{2006-smt}{Brockett, C. and Dolan, W. and Gamon, M. 2006. Correcting ESL errors Using Phrasal SMT Techniques. \emph{In Proceedings of the 21st International Conference on Computational Linguistics and the 44th annual meeting of the Association for Computational Linguistics}, 249-56}
\makecite{Brooke and Hirst}{2011}{l8-nli}{Brooke, J. and Hirst, G. 2011. Native Language Detection with `Cheap' Learner Corpora. \emph{In Proceedings of the 2011 Conference on Learner Corpus Research }, 37-47}
\makecite{Brooke and Hirst}{2012}{2012-robust-nli}{Brooke, J. and Hirst, G. 2012. Robust, Lexicalized Native Language Identification. \emph{In Proceedings of the International Conference on Computational Linguistics}, 391-408}
\makecite{Cahill, Madnani, Tetreault, and Napolitano}{2013}{wiki-rev}{Cahill, A. and Madnani, N. and Tetreault, J. and Napolitano, D. 2013. Robust Systems for Preposition Error Correction Using Wikipedia Revisions. \emph{In Proceedings of the 2013 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies}, 507--17}
\makecite{Chodorow, Dickinson, Israel, and Tetreault}{2012}{gec-eval}{Chodorow, M. and Dickinson, M. and Israel, R. and Tetreault, J. 2012. Problems in Evaluating Grammatical Error Detection Systems. \emph{In Proceedings of COLING 2012}, 611-28}
\makecite{Corston-Oliver, Gamon, and Brockett}{2001}{mt-eval}{Corston-Oliver, S. and Gamon, M. and Brockett, C. 2001. A Machine Learning Approach to the Automatic Evaluation of Machine Translation. \emph{In Proceedings of the 39th Annual Meeting on Association for Computational Linguistics}, 148-55}
\makecite{Dahlmeier and Ng}{2011a}{sem-col}{Dahlmeier, D. and Ng, H. 2011. Correcting Semantic Collocation Errors with L1-induced Paraphrases. \emph{In Proceedings of the Conference on Empirical Methods in Natural Language Processing}, 107-17}
\makecite{Dahlmeier and Ng}{2011b}{gec-alt-struct}{Dahlmeier, D. and Ng, H. 2011. Grammatical Error Correction with Alternating Structure Optimization. \emph{In Proceedings of the 49th Annual Meeting of the Association for Computational Linguistics: Human Language Technologies - Volume 1}, 915-23}
\makecite{Dahlmeier, Ng, and Wu}{2013}{nucle}{Dahlmeier, D. and Ng, H. and Wu, S. 2013. Building a Large Annotated Corpus of Learner English: The NUS Corpus of Learner English. \emph{In Proceedings of the 8th Workshop on Innovative Use of NLP for Building Educational Applications}, 22-31}
\makecite{Felice, Yuan, Andersen, Yannakoudakis, and Kochmar}{2014}{2014-hybrid}{Felice, M. and Yuan, Z. and Andersen, {\O}. and Yannakoudakis, H. and Kochmar, E. 2014. Grammatical Error Correction using Hybrid Systems and Type Filtering. \emph{In Proceedings of the Eighteenth Conference on Computational Natural Language Learning: Shared Task}, 15-24}
\makecite{Gamon}{2010}{2010-article-preposition}{Gamon, M. 2010. Using Mostly Native Data to Correct Errors in Learners' Writing: A Meta-classifier Approach. \emph{In Proceedings of Human Language Technologies: The 2010 Annual Conference of the North American Chapter of the Association for Computational Linguistics}, 163-71}
\makecite{Gamon, Aue, and Smets}{2005}{mt-eval-2}{Gamon, M. and Aue, A. and Smets, M. 2005. Sentence-level MT Evaluation Without Reference Translations: Beyond Language Modeling. \emph{In Proceedings of the European Association for Machine Translation (EAMT)}, 103-11}
\makecite{Granger}{2003}{icle}{Granger, S. 2003. The International Corpus of Learner English: A new resource for foreign language learning and teaching and second language acquisition research. \emph{In Teachers of English to Speakers of Other Languages Quarterly}, 538-46}
\makecite{Granger, Dagneaux, Meunier, and Paquot}{2009}{iclev2}{Granger, S. and Dagneaux, E. and Meunier, F. and Paquot, M. 2009. The International Learner Corpus of English, Version 2. \emph{Presses Universitaires de Louvain}.}
\makecite{Gui and Yang}{2003}{clec}{Gui, S. and H. Yang, H. 2003. Zhongguo Xuexizhe Yingyu Yuliaohu (Chinese Learner English Corpus). \emph{In Shanghai Waiyu Jiaoyu Chubanshe}}
\makecite{Guthrie, Allison, Liu, Guthrie, and Wilks}{2006}{skipgrams}{Guthrie, D. and Allison, B. and Liu, W. and Guthrie, L. and Wilks, Y. 2006. A Closer Look at Skip-gram Modelling. \emph{In Proceedings of the Fifth International Conference on Language Resources and Evaluation (LREC'06)}, 101-11}
\makecite{Han, Chodorow, and Leacock}{2006}{2006-detecting}{Han, N. and Chodorow, M. and Leacock, C. 2006. Detecting errors in English article usage by non-native speakers. \emph{Natural Language Engineering}, 115-29}
\makecite{Hermet and D{\'e}silets}{2009}{2009-correcting-prepositions}{Hermet, M. and D{\'e}silets, A. 2009. Using First and Second Language Models to Correct Preposition Errors in Second Language Authoring. \emph{In Proceedings of the Fourth Workshop on Innovative Use of NLP for Building Educational Applications}, 64-72}
\makecite{Ionescu, Popescu, and Cahill}{2014}{improv-sk}{Ionescu, R. and Popescu, M. and Cahill, A. 2014. Can Characters Reveal Your Native Language? A Language-Independent Approach to Native Language Identification. \emph{In Proceedings of the 2014 Conference on Empirical Methods in Natural Language Processing}, 1363-73}
\makecite{Ishikawa}{2009}{ceeaus}{Ishikawa, S. 2009. Vocabulary in Interlanguage: A Study on Corpus of English Essays Written by Asian University Students (CEEAUS). \emph{In Phraseology: Corpus Linguistics and Lexicology}, 87-100}
\makecite{Ishikawa}{2013}{icnale}{Ishikawa, S. 2013. The ICNALE and Sophisticated Contrastive Interlanguage Analysis of Asian Learners of English. \emph{In Learner corpus studies in Asia and the world}. 91-118}
\makecite{Jarvis, Bestgen, and Pepper}{2013}{jarvis}{Jarvis, S. and Bestgen, Y. and Pepper, S. 2013. Maximizing Classification Accuracy in Native Language Identification. \emph{In Proceedings of the Eighth Workshop on Innovative Use of NLP for Building Educational Applications}, 111-18}
\makecite{Johnson, Griffiths, and Goldwater}{2006}{adaptor-grammars}{Johnson, M. and Griffiths, T. and Goldwater, S. 2006. Adaptor Grammars: A Framework for Specifying Compositional Nonparametric Bayesian Models. \emph{In Neural Information Processing Systems}, 641-8}
\makecite{Kao, Chang, Chiu, Yen, Boisson, Wu, and Chang}{2013}{2013-task-nthu}{Kao, T. and Chang, Y. and Chiu, H. and Yen, T. and Boisson, J. and Wu, J. and Chang, J. 2013. CoNLL-2013 Shared Task: Grammatical Error Correction NTHU System Description. \emph{In Proceedings of the Seventeenth Conference on Computational Natural Language Learning: Shared Task}, 20-25}
\makecite{Koppel, Schler, and Zigdon}{2005}{koppel2005}{Koppel, M. and Schler, J. and Zigdon, K. 2005. Determining an author's native language by mining a text for errors. \emph{In Proceedings of the eleventh ACM SIGKDD international conference on Knowledge discovery in data mining}, 624-8}
\makecite{Koppel, Schler, and Argamon}{2009}{koppel-survey}{Koppel, M. and Schler, J. and Argamon, S. 2009. Computational Methods in Authorship Attribution. \emph{In the Journal of the American Society for Information Science and Technology}, 9-26}
\makecite{Kukich}{1992}{1992-spelling}{Kukich, K. 1992. Techniques for Automatically Correcting Words in Text. \emph{In ACM Computing Surveys}, 377-439}
\makecite{Kyle, Crossley, Dai, and McNamara}{2013}{nli-dfa}{Kyle, K. and Crossley, S. and Dai, J. and McNamara, D. 2013. Native Language Identification: A Key N-gram Category Approach. \emph{In Proceedings of the Eighth Workshop on Innovative Use of NLP for Building Educational Applications}, 242-50}
\makecite{Lavergne, Illouz, Max, and Nagata}{2013}{nli-mt}{Lavergne, T. and Illouz, G. and Max, A. and Nagata, R. 2013. LIMSI's participation to the 2013 shared task on Native Language Identification. \emph{In Proceedings of the Eighth Workshop on Innovative Use of NLP for Building Educational Applications}, 260-65}
\makecite{Leacock, Chodorow, Gamon, and Tetreault}{2014}{leacock-survey}{Leacock, C. and Chodorow, M. and Gamon, M. and Tetreault, J. 2014. Automated Grammatical Error Detection for Language Learners, Second Edition. \emph{Morgan and Claypool (Synthesis lectures on human language technologies), edited by Graeme Hirst}.}
\makecite{Lee and Seneff}{2006}{2006-agc}{Lee, J. and Seneff, S. 2006. Automatic Grammar Correction for Second-language Learners. \emph{In Proceedings of the 9th International Conference on Spoken Language Processing}, 1978-81}
\makecite{Madnani, Tetreault, and Chodorow}{2012}{bea-gtrans}{Madnani, N. and Tetreault, J. and Chodorow, M. 2012. Exploring Grammatical Error Correction with Not-So-Crummy Machine Translation. \emph{In Proceedings of the Seventh Workshop on Building Educational Applications Using NLP}, 44-53}
\makecite{Massung, Zhai, and Hockenmaier}{2013}{massung}{Massung, S. and Zhai, C. and Hockenmaier, J. 2013. Structural Parse Tree Features for Text Representation. \emph{In Proceedings of the International Conference on Semantic Computing}, 9-16}
\makecite{Bykh and Meurers}{2014}{nli-ensemble}{Bykh, S. and Meurers, D. 2014. Exploring Syntactic Features for Native Language Identification: A Variationist Perspective on Feature Encoding and Ensemble Optimization. \emph{In Proceedings of COLING 2014, the 25th International Conference on Computational Linguistics: Technical Papers}, 1962-73}
\makecite{Ng, Wu, Briscoe, Hadiwinoto, Sustano, and Bryant}{2014}{2014-task-all}{Ng, H. and Wu, S. and Briscoe, T. and Hadiwinoto, C. and Sustano, R. and Bryant, C. 2014. The CoNLL-2014 Shared Task on Grammatical Error Correction. \emph{In Proceedings of the Eighteenth Conference on Computational Natural Language Learning: Shared Task}, 1-14}
\makecite{Ng, Wu, Wu, Hadiwinoto, and Tetreault}{2013}{2013-task-all}{Ng, H. and Wu, S. and Wu, Y. and Hadiwinoto, C. and Tetreault, J. 2013. The CoNLL-2013 Shared Task on Grammatical Error Correction. \emph{In Proceedings of the Seventeenth Conference on Computational Natural Language Learning: Shared Task}, 1-12}
\makecite{Popescu and Ionescu}{2013}{2013-stringkernel}{Popescu, M. and Ionescu, T. 2013. The Story of the Characters, the DNA and the Native Language. \emph{In Proceedings of the Eighth Workshop on Innovative Use of NLP for Building Educational Applications}, 270-78}
\makecite{Rangel, Rosso, Chugur, Potthast, Trenkmann, Stein, Verhoeven, and Daelemans}{2014}{pan-2014}{Rangel, F. and Rosso, F. and Chugur, I. and Potthast, M. and Trenkmann, M. and Stein, B. and Verhoeven, B. and Daelemans, W. 2014. Overview of the 2nd Author Profiling Task at PAN 2014. \emph{In Proceedings of the Conference and Labs of the Evaluation Forum (Working Notes)}}
\makecite{Rozovskaya and Roth}{2010}{2010-paradigms}{Rozovskaya, A. and Roth, D. 2010. Training Paradigms for Correcting Errors in Grammar and Usage. \emph{In Proceedings of Human Language Technologies: The 2010 Annual Conference of the North American Chapter of the Association for Computational Linguistics}, 154-62}
\makecite{Rozovskaya and Roth}{2013}{2013-joint}{Rozovskaya, A. and Roth, D. 2013. Joint Learning and Inference for Grammatical Error Correction. \emph{In Proceedings of Empirical Methods in Natural Language Processing}, 791-802}
\makecite{Rozovskaya, Chang, Sammons, and Roth}{2013}{2013-task-uiuc}{Rozovskaya, A. and Chang, K. and Sammons, M. and Roth, D. 2013. The University of Illinois system in the CoNLL-2013 shared task. \emph{In Proceedings of the Seventeenth Conference on Computational Natural Language Learning: Shared Task},13-19}
\makecite{Rozovskaya, Chang, Sammons, Roth, and Habash}{2014}{2014-cuui}{Rozovskaya, A. and Chang, K. and Sammons, M. and Roth, D. and Habash, N. 2014. The Illinois-Columbia System in the CoNLL-2014 Shared Task. \emph{In Proceedings of the Eighteenth Conference on Computational Natural Language Learning: Shared Task}, 34-42}
\makecite{Stamatatos}{2009}{aa-survey}{Stamatatos, E. 2009. A survey of modern authorship attribution methods. \emph{In the Journal of the American Society for Information Science and Technology}, 538-56}
\makecite{Stolerman, Caliskan, and Greenstadt}{2013}{family}{Stolerman, A. and Caliskan, A. and Greenstadt, R. 2013. From Language to Family and Back: Native Language and Language Family Identification from English Text. \emph{In Proceedings of the 2013 NAACL HLT Student Research Workshop}, 32-9}
\makecite{Swanson and Charniak}{2012}{swanson}{Swanson, B. and Charniak, E. 2012. Native Language Detection with Tree Substitution Grammars. \emph{In Proceedings of the 50th Annual Meeting of the Association for Computational Linguistics: Short Papers - Volume 2}, 193-97}
\makecite{Tajiri, Komachi, and  Matsumoto}{2012}{l8-gec}{Tajiri, T.  and  Komachi, M.  and  Matsumoto, Y. 2012. Tense and Aspect Error Correction for ESL Learners Using Global Context. \emph{In Proceedings of the 50th Annual Meeting of the Association for Computational Linguistics (Volume 2: Short Papers)}, 198-202}
\makecite{Tetreault, Blanchard, and Cahill}{2013}{nli-shared}{Tetreault, J. and Blanchard, D. and Cahill, A. 2013. A Report on the First Native Language Identification Shared Task. \emph{In Proceedings of the Eighth Workshop on Innovative Use of NLP for Building Educational Applications}, 48-57}
\makecite{Tsur and Rappoport}{2007}{tsur}{Tsur, O. and Rappoport, A. 2007. Using Classifier Features for Studying the Effect of Native Language on the Choice of Written Second Language Words. \emph{In Proceedings of the Workshop on Cognitive Aspects of Computational Language Acquisition}, 9-16}
\makecite{Tsvetkov, Twitto, Schneider, Ordan, Faruqui, Chahuneau, Wintner, and Dyer}{2013}{nli-passives}{Tsvetkov, Y. and Twitto, N. Schneider, N. Ordan, N. and Faruqui, M. and Chahuneau, V. and Wintner, S. and Dyer, C. 2013. Identifying the L1 of Non-Native Writers: the CMU-Haifa System. \emph{In Proceedings of the Eighth Workshop on Innovative Use of NLP for Building Educational Applications}, 279-87}
\makecite{West, Park, and Levy}{2011}{2011-brw}{West, R. and Park, A. and Levy, R. 2011. Bilingual Random Walk Models for Automated Grammar Correction of ESL Author-produced Text. \emph{In Proceedings of the 6th Workshop on Innovative Use of NLP for Building Educational Applications}, 170-79}
\makecite{Wong and Dras}{2009}{wong2009contrastive}{Wong, J. and Dras, M. 2009. Contrastive analysis and native language identification. \emph{In Australasian Language Technology Association Workshop 2009}, 53-61}
\makecite{Wong and Dras}{2011}{wong-rules}{Wong, J. and Dras, M. 2011. Exploiting Parse Structures for Native Language Identification. \emph{In Proceedings of the Conference on Empirical Methods in Natural Language Processing}, 1600-10}
\makecite{Wong, Dras, and Johnson}{2012}{wong-adaptors}{Wong, J and Dras, M. and Johnson, M. 2012. Exploring Adaptor Grammars for Native Language Identification. \emph{In Proceedings of the 2012 Joint Conference on Empirical Methods in Natural Language Processing and Computational Natural Language Learning}, 699-709}
\makecite{Xiang, Yuan, Zhang, Wang, Zheng, and Wei}{2013}{2013-task-hit}{Xiang, Y. and Yuan, B. and Zhang, Y. and Wang, X. and Zheng, W. and  Wei, C. 2013. A Hybrid Model For Grammatical Error Correction. \emph{In Proceedings of the Seventeenth Conference on Computational Natural Language Learning: Shared Task}, 115-22}
\makecite{Yannakoudakis, Briscoe, and Medlock}{2011}{fce-dataset}{Yannakoudakis, H and Briscoe, T and Medlock, B. 2011. A New Dataset and Method for Automatically Grading ESOL Texts. \emph{In Proceedings of the 49th Annual Meeting of the Association for Computational Linguistics: Human Language Technologies}, 180-89}
\makecite{Yu, Lee, and Chang}{2014}{tea}{Yu, L. and Lee, L. and Chang, L. 2014. Overview of Grammatical Error Diagnosis for Learning Chinese as a Foreign Language. \emph{In Proceedings of the 22nd International Conference on Computers in Education}, 42-7}
