% rubber: setlist arguments --shell-escape
\documentclass{nle}

\newcommand{\makecite}[4]{\bibitem[\protect(\citename{#1 }#2)]{#3}#4}
\usepackage{graphicx,color,amssymb,times}
\usepackage[hidelinks]{hyperref}

\newcommand{\textoverline}[1]{$\overline{\mbox{#1}}$}

\title{Non-Native Text Analysis: A Survey}
\author[Sean Massung and ChengXiang Zhai]{SEAN MASSUNG and CHENGXIANG ZHAI \\
    Department of Computer Science \\
College of Engineering \\ University of Illinois at Urbana-Champaign \\
\texttt{\{massung1,czhai\}@illinois.edu}}
\received{25 November 2014; revised 12 March, 18 May, and 16 July 2015;\\
    accepted 20 July 2015}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\pubyear{2015}

\newcommand{\todo}[1]{}
\renewcommand{\todo}[1]{{\color{red} TODO: {#1}}}

\begin{document}
\label{firstpage}
\maketitle

\begin{abstract}
Non-native speakers of English far outnumber native speakers; English is the
main language of books, newspapers, airports, air-traffic control, international
business, academic conferences, science, technology, diplomacy, sports,
international competitions, pop music, and advertising (British Council 2014).
Online education in the form of MOOCs (massive online open courses) is also
primarily in English---even teaching English. This creates enormous amounts of
text written by non-native speakers, which in turn generates a need for grammar
correction and analysis. Even aside from MOOCs, the number of English learners
in Asia alone is in the tens of millions.

In this paper, we provide a survey of the two main areas of existing work on
non-native text analysis, prefaced by an overview of common datasets used by
researchers, comparing their attributes and potential uses. Then, an
introduction to native language identification follows: determining the native
language of an author based on text in the second language. This section is
subdivided into various techniques and a shared task on this classification
problem. Next, we discuss non-native grammatical error correction---finding and
modifying text to fix errors or to make it sound more fluent. Again, we discuss
different methods before investigating a relevant shared task. Lastly, we end
with conclusions and potential future directions. While this survey primarily
focuses on detecting and correcting non-native \emph{English} text, many
approaches are general and can be used across any language pairing.
\end{abstract}

\input{introduction}
\input{datasets}
\input{nli}
\input{grammar}
\input{conclusion}

\begin{thebibliography}{}
    \input{manualbib}
\end{thebibliography}
\label{lastpage}
\end{document}
